---
title: "week_05_day_02_homework"
output: html_notebook
editor_options: 
  chunk_output_type: console
---

```{r}
library(tidyverse)
library(CodeClanData)
```

```{r}
backpack <- CodeClanData::backpack
```

# Qu. 1 ----

```{r}
view(backpack)
dim(backpack)
summary(backpack)
```

# Qu. 2 ----

The data looks almost like a bell curve or normal distribution, minus a few outliers.

```{r}
backpack %>% 
  ggplot() +
  aes(x = backpack_weight) +
  geom_histogram(fill = "purple", colour = "white") +
  labs(
    x = "Backpack Weight",
    y = "Count",
    title = "Backpack Weight Distribution"
  ) +
  theme_bw()
```

# Qu. 3 ----

Again, the distributions appears to be a normal distribution...ish.
It would appear from the graphs that males carry only slightly heavier backpacks. 
For females, the average weight is 11 and for the males, 12.4. 

```{r}
backpack %>% 
  ggplot() +
  aes(x = backpack_weight) +
  geom_histogram(fill = "purple", colour = "white") +
  labs(
    x = "Backpack Weight",
    y = "Count",
    title = "Backpack Weight Distribution",
    subtitle = "by sex"
  ) +
  facet_wrap(~ sex) +
  theme_bw()

# lets check the average values for both females and males!
backpack %>% 
  group_by(sex) %>% 
  summarise(avg_weight = mean(backpack_weight))
```

# Qu. 4 ----

As body weight increases to a point, backpack weight also increases. After this point
back pack weight decreases.

```{r}
backpack %>% 
  ggplot() +
  aes(x = body_weight, y = backpack_weight) +
  geom_line() +
  geom_smooth() +
  theme_bw()
```

# Qu. 5 ----

There is a relationship between body weight and backpack weight for both sexes,
i.e. backpack weight increases with body weight but it is subtle. For the males, 
backpack weight actually begins to decrease over body weight of 200, for females 
the relationship is quite stable.

```{r}
backpack %>% 
  ggplot() +
  aes(x = body_weight, y = backpack_weight) +
  geom_point() +
  geom_smooth() +
  facet_wrap(~ sex, ncol = 1) +
  labs(
    x = "Body Weight",
    y = "Backpack Weight",
    title = "Backpack Weight vs. Body Weight",
    subtitle = "Split by sex"
  ) +
  theme_bw()
```

# Qu. 6 ----

32% of people in the backpack dataset reported that they suffer from back pain.

```{r}
backpack %>%
  group_by() %>% 
  summarise(back_pain = sum(back_problems) / n())

backpack %>%
  mutate(has_back_problems = case_when(
    back_problems == 1 ~ "back_problems",
    back_problems == 0 ~ "no_back_problems"
  )) %>% 
  ggplot() +
  aes(x = has_back_problems) +
  geom_bar(fill = "lightblue") +
  labs(
    x = "Back Problems",
    y = "Count",
    title = "Proportion of those with back problems"
  ) +
  theme_bw()
```

# Qu. 7 -----

24% of females and 8% of males in the dataset suffer from back problems.

```{r}
backpack %>%
  mutate(has_back_problems = case_when(
    back_problems == 1 ~ "back_problems",
    back_problems == 0 ~ "no_back_problems"
  )) %>% 
  ggplot() +
  aes(x = has_back_problems) +
  geom_bar(fill = "lightblue") +
  facet_wrap(~ sex) +
  labs(
    x = "Back Problems",
    y = "Count",
    title = "Proportion of those with back problems",
    subtitle = "split by sex"
  ) +
  theme_bw()
```

# Qu. 8 ----

```{r}
backpack %>%
  mutate(has_back_problems = case_when(
    back_problems == 1 ~ "back_problems",
    back_problems == 0 ~ "no_back_problems"
  )) %>% 
  ggplot() +
  aes(x = body_weight, y = backpack_weight, shape = sex) +
  geom_point(colour = "lightsalmon3", alpha = 0.5) +
  facet_wrap(~ has_back_problems) +
  labs(
    x = "Body Weight",
    y = "Backpack Weight",
    title = "Body Weight vs. Backpack Weight",
    subtitle = "split by sex and reported back problems"
  ) +
  theme_bw()
```

# Ext. Qu. 1 ----

Year 3 has the highest number of students who reported they suffer from back problems.
No students from year 6 reported any back problems. 

```{r}
backpack %>%
    filter(year != 0) %>% 
    mutate(has_back_problems = case_when(
    back_problems == 1 ~ "back_problems",
    back_problems == 0 ~ "no_back_problems"
  )) %>% 
  ggplot() +
  aes(x = has_back_problems) +
  geom_bar(fill = "plum4") +
  facet_wrap(~ year) +
  labs(
    x = "Reported Back Problems",
    y = "No. of Students",
    title = "Relationship between Back Pain and Year Groups"
  ) +
  theme_bw()
```

# Ext. Qu. 2 ----

```{r}
backpack %>%
  filter(year != 0) %>%
  group_by(year) %>% 
  summarise(avg_backpack_weight = mean(backpack_weight)) %>% 
  ggplot() +
  aes(x = year, y = avg_backpack_weight) +
  geom_line(colour = "burlywood4") +
  labs(
    x = "\nSchool Year",
    y = "Average Backpack Weight\n",
    title = "Backpack Weight vs Year"
  ) +
  scale_x_continuous(breaks = 1:6) +
  theme_bw()
```

