---
title: "week_01_homework"
output:
  pdf_document: default
  html_notebook: default
---
# Load in Tidyverse & Lubridate library

```{r}
library(tidyverse)
library(lubridate)
library(ggplot2)
```

# Assign books.csv to books_df

```{r}
books_df <- read_csv("data/books.csv")
```

# Perform some initial checks and view dataframe

```{r}
str(books_df)
```

```{r}
glimpse(books_df)
```

```{r}
names(books_df)
```

```{r}
books_df %>% 
  summarise(
    na_count = sum(is.na(.))
    )
```
# remove rows with average_rating == 0 or num_pages == 0 and rename cols/rows

```{r}
books_df1 <- books_df %>% 
  filter(average_rating != 0, num_pages != 0) %>% 
    rename("row_id"  = "rowid",
         "book_id" = "bookID",
         "isbn_13" = "isbn13",
         ) %>% 
  mutate(language_code = recode(language_code,
                                "eng"   = "en",
                                "en-US" = "en-us",
                                "en-GB" = "en-gb",
                                "en-CA" = "en-ca"))
books_df1
```

# Convert publication_date from character type to date ?????

```{r}
# books_df1 %>% 
#   mdy(publication_date, format = "%m/%d/%Y")
```

# average rating per author top 10

```{r}
books_author_ratings <- books_df1 %>% 
  group_by(authors) %>% 
  summarise(avg_rating = mean(average_rating[average_rating != 0]), 
            sum_books = n()) %>%
  filter(sum_books >= 2) %>%
  arrange(desc(avg_rating)) %>% 
  head(10)

books_author_ratings
```

# books published by publisher

```{r}
books_df1 %>% 
  group_by(publisher) %>% 
  summarise(books_published = n(), 
            avg_rating = mean(average_rating[average_rating != 0])) %>% 
  arrange(desc(books_published)) %>% 
  head(10)
```

# top 10 books written by author

```{r}
books_df1 %>% 
  group_by(authors) %>%
  summarise(count= n(), 
            avg_rating = mean(average_rating[average_rating != 0])) %>% 
  arrange(desc(count)) %>% 
  head(10)
```

# Stephen King top 5/bottom 5 books

```{r}
books_sk <- books_df1 %>% 
  filter(authors == "Stephen King") %>%
  select(title, average_rating, ratings_count, publication_date, num_pages, 
         publisher) %>%
  arrange(desc(average_rating)) %>% 
  distinct(title, .keep_all = TRUE) 
 
head(books_sk, n = 5)
tail(books_sk, n = 5)
```

# Stephen King books by publisher

```{r}
books_sk_pub <- books_sk %>%
  group_by(publisher) %>% 
  mutate(publisher = recode(publisher, "New English Library (Hodder & Stoughton)"
                                                     = "New English Library",
                            "Hodder & Stoughton Ltd" = "New English Library",
                            "Hodder & Stoughton"     = "New English Library",
                            "Simon & Schuster Audio" = "Simon Schuster Audio",
                            "Doubleday"              = "Doubleday Books",
                            "Pocket"                 = "Pocket Books",
                            "Viking"                 = "Viking Books",
                            "Signet"                 = "Penguin Signet")) %>% 
  summarise(no_of_books = n()) %>% 
  arrange(desc(no_of_books))
books_sk_pub
```

# parsing dates ????

```{r}
books_sk_date <- books_sk %>%
  select(title, average_rating, ratings_count, publication_date, num_pages, publisher) %>%
  mutate(publication_date = as.Date(publication_date, format = "%m/%d/%Y")) %>%
  distinct(publication_date) %>%
  mutate(year = floor_date(publication_date, "year"))
books_sk_date

typeof(books_sk_date$publication_date)
class(books_sk_date$publication_date)
```






