---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(modelr)
library(GGally)
library(ggfortify)
library(relaimpo)
library(lm.beta)
```

# MVP 1

```{r}
# read in dataset
house_data <- read_csv("data/kc_house_data.csv") 

# clean dataset
house_tidy <- house_data %>% 
  dplyr::select(-c(date, id, sqft_living15, sqft_lot15, zipcode)) %>% 
  mutate(yr_renovated = ifelse(yr_renovated == 0, FALSE, TRUE)) %>% 
  mutate(waterfront = ifelse(waterfront == 0, FALSE, TRUE)) %>% 
  rename("renovated" = "yr_renovated") %>% 
  mutate(grade = ifelse(grade <= 3, "poor", ifelse(grade <= 7, "average", "good")))
  
```

# MVP 2

```{r}
# use alias() to check for any variables that lead to an alias
alias(lm(price ~ ., data = house_tidy))
```

```{r}
# remove sqft_basement
house_tidy <- house_tidy %>% 
  dplyr::select(-sqft_basement)

# rerun alias to check that there are now no aliases
alias(lm(price ~ ., data = house_tidy))
```

# MVP 3

```{r}
house_tidy_numeric <- house_tidy %>%
  select_if(is.numeric)

house_tidy_nonnumeric <- house_tidy %>%
  select_if(function(x) !is.numeric(x))

house_tidy_nonnumeric$price <- house_tidy$price

ggpairs(house_tidy_numeric)
ggpairs(house_tidy_nonnumeric)
```
# 1st Predictor 

```{r}
# first model price ~ sqft_living
mod_1 <- lm(price ~ sqft_living, data = house_tidy)

summary(mod_1)

par(mfrow = c(2, 2))
plot(mod_1)
```

```{r}
# second model price ~ sqft_above
mod_2 <- lm(price ~ sqft_above, data = house_tidy)

summary(mod_2)

par(mfrow = c(2, 2))
plot(mod_2)
```
sqft_living will be used as the first predictor since the r2 value is higher, 50% vs 36%, diagnostics for both models look ok-ish but not great!

# Second predictor

```{r}
prestige_remaining_resid <- house_tidy %>%
  add_residuals(mod_1) %>%
  dplyr::select(-c("price", "sqft_living"))

prestige_remaining_resid %>%
  ggpairs(aes(colour = waterfront, alpha = 0.5))
```

```{r}
mod_3 <- lm(price ~ sqft_living + yr_built, data = house_tidy)

summary(mod_3)

par(mfrow = c(2, 2))
plot(mod_3)
```

```{r}
mod_4 <- lm(price ~ sqft_living + lat, data = house_tidy)

summary(mod_4)

par(mfrow = c(2, 2))
plot(mod_4)
```
Second predictor will be lat as it gives a slight higher r2 value, 56% vs 52% for yr_built. The diagnostics are almost identical.

# Third predictor

```{r}
prestige_remaining_resid <- house_tidy %>%
  add_residuals(mod_4) %>%
  dplyr::select(-c("price", "sqft_living", "lat"))

prestige_remaining_resid %>%
  ggpairs(aes(colour = waterfront, alpha = 0.5))
```

```{r}
mod_5 <- lm(price ~ sqft_living + lat + view, data = house_tidy)

summary(mod_5)

par(mfrow = c(2, 2))
plot(mod_5)
```

```{r}
mod_6 <- lm(price ~ sqft_living + lat + yr_built, data = house_tidy)

summary(mod_6)

par(mfrow = c(2, 2))
plot(mod_6)
```
For the third predictor we will choose view over lat as it provide the higher r2 value.

# Forth predictor

```{r}
house_resid <- house_tidy %>% 
  add_residuals(mod_5) %>% 
  dplyr::select(-price)

coplot(resid ~ sqft_living | lat, 
       panel = function(x, y, ...){
         points(x, y)
         abline(lm(y ~ x), col = "blue")
       }, 
       data = house_resid, 
       columns = 6)

coplot(resid ~ lat | view, 
       panel = function(x, y, ...){
         points(x, y)
         abline(lm(y ~ x), col = "blue")
       }, 
       data = house_resid, 
       columns = 6)

coplot(resid ~ sqft_living | view, 
       panel = function(x, y, ...){
         points(x, y)
         abline(lm(y ~ x), col = "blue")
       }, 
       data = house_resid, 
       columns = 6)
```

