---
title: "R Notebook"
output: html_notebook
---

```{r}
library(prob)
library(tidyverse)
library(janitor)
library(MASS)
```

# Qu. 1 ----

```{r}
mobile_data <- read_csv("data/20190928-items.csv")

glimpse(mobile_data)
head(mobile_data)
summary(mobile_data)
```

# Qu.2 ----

```{r}
mobile_data %>% 
  group_by(brand) %>% 
  summarise(count = n()) %>% 
  arrange(desc(count))
```

# Qu.3 ----

```{r}
# cfilter to only show Samsung phones
samsung_data <- mobile_data %>%
  filter(brand == "Samsung")

# calculate the mean and std deviation of Samsung phones
samsung_phone_stats <- samsung_data %>% 
  summarise(num = n(),
            mean = mean(rating),
            sd = sd(rating)
            )

# create histogram with a density scale, use stat_function to add the dnorm fn
# to the histogram with the mean and std dev set to the calc'd values above
samsung_data %>% 
  ggplot(aes(x = rating)) +
  geom_histogram(aes(y = ..density..), col = "white", bins = 25) +
  stat_function(
    fun = dnorm,
    args = list(
      mean = samsung_phone_stats$mean,
      sd = samsung_phone_stats$sd
    ), 
    col = "red"
  )
```

The normal distribution appears to be a good fit for our data, although it is a bit left skewed,
this is a result of those 1 ratings. 

# Qu.4 ----

```{r}
# creating new column for z scores. A z-score gives  an idea of how far from the mean a data point is. 
samsung_mobile_data_scaled <- samsung_data %>% 
  mutate(z_rating = scale(rating))

# calc the proportion of observations within 1 sd
samsung_mobile_data_scaled %>% 
  dplyr::select(title, rating, z_rating) %>% 
  filter(between(z_rating, left = -1, right = 1)) %>% 
  summarise(proportion = n() / nrow(samsung_data))

# calc the proportion of observations within 2 sd
samsung_mobile_data_scaled %>% 
  dplyr::select(title, rating, z_rating) %>% 
  filter(between(z_rating, left = -2, right = 2)) %>% 
  summarise(proportion = n() / nrow(samsung_data))

# calc the proportion of observations within 3 sd
samsung_mobile_data_scaled %>% 
  dplyr::select(title, rating, z_rating) %>% 
  filter(between(z_rating, left = -3, right = 3)) %>% 
  summarise(proportion = n() / nrow(samsung_data))
```

Calculated proportions of ratings:
  1 sd - 79.3% compared to an expected value of 68% of observations within 1 sd
  2 sd - 91.9% compared to an expected value of 95% of observation within 2 sd
  3 sd - 97.9% compared to an expected value of >99% of observations with 3 sd
  
Suggests that our data does not exactly fit within a normal distribution but there 
is a good fit, perhaps filtering out the outlier reviews would yield better agreement. 

```{r}
# expected distributions of observations for a normal distribution
100 * (pnorm(q = 1) - pnorm(q = -1))
100 * (pnorm(q = 2) - pnorm(q = -2))
100 * (pnorm(q = 3) - pnorm(q = -3))
```

# re-do with the outliers removed...

```{r}
# remove outliers from dataset
samsung_data_outliers_rm <- samsung_mobile_data_scaled %>% 
  filter(between(z_rating, left = -3, right = 3))

# calc new mean and sd
samsung_stats_outliers_rm <- samsung_data_outliers_rm %>% 
  summarise(num = n(),
            mean = mean(rating),
            sd = sd(rating)
            )

# create histogram with a density scale, use stat_function to add the dnorm fn
# to the histogram with the mean and std dev set to the calc'd values above
samsung_data_outliers_rm %>% 
  ggplot(aes(x = rating)) +
  geom_histogram(aes(y = ..density..), col = "white", bins = 25) +
  stat_function(
    fun = dnorm,
    args = list(
      mean = samsung_stats_outliers_rm$mean,
      sd = samsung_stats_outliers_rm$sd
    ), 
    col = "red"
  )

samsung_data_scaled_rm <- samsung_data_outliers_rm  %>% 
  mutate(z_rating = scale(rating))

samsung_data_scaled_rm %>% 
  dplyr::select(title, rating, z_rating) %>% 
  filter(between(z_rating, left = -1, right = 1)) %>% 
  summarise(proportion = n() / nrow(samsung_data_outliers_rm))

samsung_data_scaled_rm %>% 
  dplyr::select(title, rating, z_rating) %>% 
  filter(between(z_rating, left = -2, right = 2)) %>% 
  summarise(proportion = n() / nrow(samsung_data_outliers_rm))

samsung_data_scaled_rm %>% 
  dplyr::select(title, rating, z_rating) %>% 
  filter(between(z_rating, left = -3, right = 3)) %>% 
  summarise(proportion = n() / nrow(samsung_data_outliers_rm))
```

Marginal improvement in the agreement between our data an expected values -
  72.7% / 79.3%
  93% / 91.9%
  100% / 97.9
Therefore identifying and removing outliers yields a small improvement in achieving 
agreement with expected values but was it worth it??? 

```{r}
qqnorm(samsung_data$rating)
qqline(samsung_data$rating)

```

```{r}
qqnorm(samsung_data_outliers_rm$rating)
qqline(samsung_data_outliers_rm$rating)
```

