---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(infer)
library(janitor)
```

# Task 1 ----

```{r}
ames <- read_csv("data/ames.csv") %>% 
  clean_names()
```

# Task 2 ----

```{r}
ames %>% 
  ggplot() +
  aes(x = lot_area) +
  geom_histogram(col = "white", bins = 50)

qqnorm(ames$lot_area)
qqline(ames$lot_area)
```
The dataset, according to the normal qq plot, is roughly normally distributed. However, there are
some significant outliers which makes me question this!

# Task 3 ----

```{r}
bootstrap_resample <- ames %>%
  specify(response = lot_area) %>% 
  generate(reps = 5000, 
           type = "bootstrap") %>% 
  calculate(stat = "mean")

bootstrap_resample %>% 
  ggplot() +
  aes(x = stat) +
  geom_histogram(col = "white", bins = 35)
```

# Task 4 ----

```{r}
bootstrap_resample_ci_95 <- bootstrap_resample %>% 
  get_ci(level = 0.95, type = "percentile") 
bootstrap_resample_ci_95

bootstrap_resample %>% 
  visualise() +
  shade_ci(endpoint = bootstrap_resample_ci_95)
```

# Task 5 ----

```{r}
bootstrap_resample_ci_99 <- bootstrap_resample %>% 
  get_ci(level = 0.99, type = "percentile") 

bootstrap_resample_ci_99
```
The higher the confidence the broader the limits. Makes sense! Greater confidence 
means considering more data, i.e. I have greater confidence that the parameter lies
within these limits.

# Task 6 ----

```{r}
mean_infer <- bootstrap_resample %>% 
  summarise(mean = mean(stat))
mean_infer
```

# Ext. 1 ----

```{r}
ames_ext_data <- ames %>% 
  filter(year_built < 1920) %>% 
  specify(response = lot_area) %>% 
  generate(reps = 200, 
           type = "bootstrap") %>% 
  calculate(stat = "mean")
ames_ext_data

ames_ext_data <- ames %>% 
  filter(year_built < 1920) %>% 
  specify(response = lot_area) %>% 
  generate(reps = 200, 
           type = "bootstrap") %>% 
  calculate(stat = "mean")
ames_ext_data

ames_ext_data %>% 
  get_ci(level = 0.95, type = "percentile") 

```

